Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
start explaining broadband model predictions

\begin{equation}
\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
\end{equation}

@@

\subsection{Unit Conversions}

The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
\verb|i100| and the higher frequency HFI maps are provided in units of 
MJy/sr.

\subsection{Fitting Parameters}
In order to fit the \PLANCK/\verb|i100| dust SED, we must combine the 
underlying two-component spectrum $M_{\nu}$ with the bandpass corrections 
$b_{\nu_i}$ to yield predictions which can be compared against the observed 
broadband intensities. The model-predicted broadband intensities 
$\tilde{I}_{\nu_i}$ are given by:

\begin{equation}
\label{eqn:inten}
\tilde{I}_{\nu_i} = \frac{b_{\nu_i}(T_2)M_{\nu_i}}{b_{545}(T_2)M_{545}}\tilde{I}_{545}
\end{equation}

We will treat the SED normalization $\tilde{I}_{545}$ as a free parameter in
our fitting procedure. In our baseline fits, second free parameter is $T_2$, 
which determines the shape of the SED through $M_{\nu}$ as well as 
$b_{\nu_i}(T_2)$.

>>>>

\begin{equation} \label{equ:broadband}
\tilde{I}_{\nu_i} \propto \sum_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k)
\end{equation}

@@

\subsection{Predicting the Observed SED}
With the formalism established in $\S$\ref{sec:modeling} and 
$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
MCMC sampling to predict the observed SED, which we will denote by 
\{$\tilde{I}_{\nu_i}$\}. The predicted broadband intensities are given by:

\begin{equation}
\label{eqn:inten}
\tilde{I}_{\nu_i} = \frac{\sum\limits_{k=1}^{2} b_{\nu_i}(T_k, \beta_k) f_k q_k (\nu_{i,c}/\nu_0)^{\beta_k} B_{\nu_{i,c}}(T_k) u_{\nu_i}^{-1}(T_k, \beta_k)}{\sum\limits_{k=1}^{2} b_{545}(T_k, \beta_k) f_k q_k (545 \textrm{GHz}/\nu_0)^{\beta_k} B_{545}(T_k)}\tilde{I}_{545}
\end{equation}

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. The first is that the normalization of 
$\tilde{I}_{\nu_i}$ is now specified by $\tilde{I}_{545}$, which represents the
 broadband intensity measured in \PLANCK~545 GHz. Also, each term in the 
numerator is multiplied by a conversion factor $u_{\nu_i}^{-1}(T_k, \beta_k)$. 
This factor is necessary because some of the \PLANCK~maps of interest have 
units of $K_{CMB}$ (100-353 GHz), while others (545-3000 GHz) have units of 
MJy/sr. Therefore, we wish to predict the low frequency bands in $K_{CMB}$, and
the high frequency bands in MJy/sr. For this reason, we evaluate $B_{\nu_i}$ in
Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for all 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr

% equation for u goes here

To reiterate, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and
therefore $I_{\nu_{i}}$ will have different units depending on the band 
$\nu_i$, though $I_{\nu_{i}}$ always has the same units as the native 
\PLANCK~HFI band $\nu_i$ map.

The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent.

% add a sentence in the middle of the previous paragraph explaining why
% it doesn't make sense to just multiply the Kcmb maps by some factor
% and pretend they're in MJy/sr for the sake of making predictions

The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
\verb|i100| and the higher frequency HFI maps are provided in units of 
MJy/sr. We will treat the SED normalization $\tilde{I}_{545}$ as a free 
parameter in our fitting procedure. In our baseline fits, second free parameter
 is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
$b_{\nu_i}(T_2)$.
